% Compile with XeLaTeX or LuaLaTeX

\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage[english]{babel}

\usepackage{datetime}

\newdateformat{monthyearformat}{\monthname[\THEMONTH] \THEYEAR}

\newcommand{\monthyear}{\monthyearformat\today}

% Personal data
\firstname{Quang}
% \middlename{Vu}
\lastname{Dao}
\email{qvd@andrew.cmu.edu}
\homepage{https://quangvdao.github.io/}
\address{}{Pittsburgh, PA}{}
\social[googlescholar][https://scholar.google.com/citations?user=pN642RkAAAAJ]{Google Scholar}
\extrainfo{Last updated: \monthyear}

\begin{document}
\makecvtitle

\vspace{-2em}

\section{Education}

\cventry{2022--Present}{Carnegie Mellon University}{Pittsburgh, PA}{}{}{
    PhD in Computer Science. \emph{Advisors:} Aayush Jain and Riad Wahby.
}

\cventry{2020--2022}{University of Michigan}{Ann Arbor, MI}{}{}{
    MA in Mathematics. \emph{Advisor:} Paul Grubbs
}

\cventry{2016--2020}{Columbia University}{New York, NY}{}{}{
    BA in Mathematics and Computer Science
}

\section{Research Interests}

\cvitem{}{My research focuses on guaranteeing the security of \textbf{zero-knowledge proof systems} in practice, and building \textbf{advanced cryptographic primitives} that are secure against quantum computers.}

\section{Publications}

% \cvitem{}{\scriptsize (* = first author)}

\cvitem{6.}{\textbf{Quang Dao}, Aayush Jain. Lossy Cryptography from Code-Based Assumptions. \textit{CRYPTO 2024}. \textbf{\textit{Best Paper from Early Career Researchers.}}}

\cvitem{5.}{\textbf{Quang Dao}, Aayush Jain, Zhengzhong Jin. Non-Interactive Zero-Knowledge from LPN and MQ. \textit{CRYPTO 2024}.}

\cvitem{4.}{\textbf{Quang Dao}, Yuval Ishai, Aayush Jain, Huijia Lin. Multi-party Homomorphic Secret Sharing and Sublinear MPC from Sparse LPN. \textit{CRYPTO 2023}.}

\cvitem{3.}{\textbf{Quang Dao}, Jim Miller, Opal Wright, Paul Grubbs. Weak Fiat-Shamir Attacks on Modern Proof Systems. \textit{IEEE S\&P 2023}. \textbf{\textit{Distinguished Paper Award.}}}

\cvitem{2.}{\textbf{Quang Dao}, Paul Grubbs. Spartan and Bulletproofs are simulation-extractable (for free!). \textit{EUROCRYPT 2023}.}

\cvitem{1.}{\textbf{Quang Dao}, Julian Wellman, Calvin Yost-Wolff, Sylvester W. Zhang. Rowmotion Orbits of Trapezoid Posets. \textit{The Electronic Journal of Combinatorics}, P2-29, 2022.}

\section{Preprints}

\cvitem{3.}{\textbf{Quang Dao}, Justin Thaler. More Optimizations for Sum-Check Proving. \textit{ePrint 2024}.}

\cvitem{2.}{\textbf{Quang Dao}, Justin Thaler. Constraint-Packing and the Sum-Check Protocol over Binary Tower Fields. \textit{ePrint 2024}.}

\cvitem{1.}{\textbf{Quang Dao}, Christina Meng, Julian Wellman, Zixuan Xu, Calvin Yost-Wolff, Teresa Yu. Extended Nestohedra and their Face Numbers. \textit{arXiv 2019}.}


\section{Fellowships \& Awards}

\cvitem{2024-2025}{
    \textbf{Quad Fellowship} \newline
    One-year fellowship for US-based PhD students in STEM fields.
    %  Selected as one of 50 fellows among 3000 applicants.
}

\cvitem{2024-2025}{
    \textbf{CyLab Fellowship} \newline
    One-year fellowship from CyLab at Carnegie Mellon University
}

\cvitem{2024}{
    \textbf{Best Paper from Early Career Researchers} \newline
    Awarded to the best paper from early career researchers at CRYPTO 2024
}

\cvitem{2023}{\textbf{Distinguished Paper Award} \newline
Awarded to top 6\% of accepted papers at IEEE Security \& Privacy 2023}

\cvitem{2020}{\textbf{Russell C. Mills Award} \newline
Awarded to 2 seniors for excellence in computer science at Columbia}

\cvitem{2017 - 2019}{\textbf{Van Amringe Math Prize} \newline
Awarded annually to the top 3 non-senior students in math at Columbia}

\cvitem{2016, 2018}{\textbf{Putnam Math Competition}. Honorable Mention (top 50)}

\cvitem{2016}{\textbf{International Math Olympiad}. Silver Medal}

\section{Internships \& Visiting Positions}
\cvitem{Summer 2024}{Research Intern at a16z crypto.}

\section{Talks}

\cvitem{6.}{Advanced Security for SNARKs: A Survey
\begin{itemize}
    \item a16z Crypto Research Seminar (Jun 2024)
\end{itemize}
}

\cvitem{5.}{Lossy Cryptography from Code-Based Assumptions
\begin{itemize}
    \item UCLA Crypto Reading Group (Apr 2024)
    \item UToronto Theory Seminar (Mar 2024)
\end{itemize}
}

\cvitem{4.}{Multi-party Homomorphic Secret Sharing and Sublinear MPC from Sparse LPN
\begin{itemize}
    \item JP Morgan AlgoCRYPT Seminar (Dec 2023)
    \item CMU Crypto Seminar (Nov 2023)
    \item NTT Research Seminar (Oct 2023)
    \item CyLab Partners Conference (Oct 2023)
    \item Vietnam Mathematical Congress (Aug 2023)
\end{itemize}
}

\cvitem{3.}{Weak Fiat-Shamir Attacks on Modern Proof Systems
\begin{itemize}
    \item Real World Crypto (Mar 2024)
    \item CMU CyLab Security Seminar (Nov 2023)
    \item Cornell Security Seminar (Sep 2023)
    \item NYU Crypto Reading Group (Sep 2023)
    \item Workshop on Attacks in Cryptography (Aug 2023)
\end{itemize}
}

\cvitem{2.}{Spartan and Bulletproofs are simulation-extractable (for free!)
\begin{itemize}
    \item Stanford Crypto Reading Group (May 2023)
    \item Telecom Paris Seminar (May 2023)
    \item Lattices Meet Hashes Workshop, EPFL (May 2023)
    \item CMU Crypto Seminar (April 2023)
\end{itemize}
}

\section{Service}

\cvitem{Co-Organizer}{2022-2024: CMU Crypto Seminar}

% \cvitem{Program Committee}{TBD}
\cvitem{External Reviewer}{
2024: STOC, EUROCRYPT, TCC
\newline
2023: ASIACRYPT, TCC, FOCS
\newline
2022: CRYPTO, EUROCRYPT}

\section{Teaching}
\cventry{2023-2024}{Western Pennsylvania ARML Team}{Assistant Coach}{CMU}{}{}
\cventry{Fall 2023}{Undergraduate Quantum Computation}{Teaching Assistant}{CMU}{}{}
\cventry{2020--2021}{Calculus I}{Lead Instructor}{University of Michigan}{}{}
\cventry{2017, 2021}{Math \& Science Summer Program (MASSP)}{Mentor}{Vietnam}{}{}

\section{Miscellaneous}
\cvitem{Languages}{English (fluent), Vietnamese (native), French (elementary), Malayalam (elementary)}
% \cvitem{Citizenship}{Vietnamese}
% \cvitem{Skills}{LaTeX, Python, Rust, Sage} 
% Trivial stuff
% \cvitem{Interests}{}


\end{document}